---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "22.12.2021"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('Group 1 GHA 4.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required libraries and the data sets are loaded 
first.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
The share of males who consume soft drugs is ~29.18%
```{r exercise_1, echo=TRUE, warning=FALSE}
```

# Exercise 2 {-}
The difference between the share of male and female hard drug consumers is ~2.74%
```{r exercise_2, echo=TRUE, warning=FALSE}
```

\pagebreak

# Exercise 3 {-}
From the shares of soft drug consumption for each age group, one can observe that only 16-17 year-olds consume soft drugs. Therefore, the consumption of soft drugs is decreasing in age, but not strictly as the groups of 18-19 and 20-24 year-olds are not consuming any soft drugs at all.
```{r exercise_3, echo=TRUE, warning=FALSE}
```

# Exercise 4 {-}
The chi-squared test results in a X-squared statistic of 9.40 at a p-value of 0.025. Hence, the hypothesis of independence is rejected (0.025 < 0.05) and the earnings range and soft drug consumption are indeed dependent at a condifence interval of 5%.
```{r exercise_4, echo=TRUE, warning=FALSE}
```

# Exercise 5 {-}
tbd
```{r exercise_5, echo=TRUE, warning=FALSE}
```


# Exercise 6 {-}
When keeping the numbers of draws fixed at 500 one can see a higher density around the mean of the whole sample (see exercise 5) with an increasing sample size. If the sample size is kept fixed at 500 and the number of draws (100, 500, 2500) is varied one can observe that the curve is smoother for higher number of draws. 
```{r exercise_6, echo=TRUE, warning=FALSE}
```