---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "15.12.2021"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('Group 1 GHA 3.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required libraries and the data sets are loaded 
first.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
The average online spending is $1959.921
```{r exercise_1, echo=TRUE, warning=FALSE}
```

# Exercise 2 {-}
The household with id = 1297 (first row of the 2006 sample) spends most of the time on *weather.com*
```{r exercise_2, echo=TRUE, warning=FALSE}
```

\pagebreak

# Exercise 3 {-}
To find the best two linear predictors, lasso was used. First, a 5-fold cross 
validation was performed to determine the optimal lambda parameter. In the plot below 
the result of the cross validation is shown. Where the minimum of the MSE is reached is 
the optimal value of the lambda parameter.
```{r exercise_3.1, echo=TRUE, warning=FALSE}
```

\pagebreak

Then, the largest coefficients in terms of their absolute value of the lasso model with
the optimal lambda from before were determined, since they have the greatest influence 
on the prediction. The best two linear predictors are therefore the two websites 
*staples.com* and *officedepot.com*.
```{r exercise_3.2, echo=TRUE, warning=FALSE}
```

# Exercise 4 {-}

```{r exercise_4, echo=TRUE, warning=FALSE}
```

What we can see in our plot is that our "all variables" model predicts a significant amount of values < 0, which is not reasonable. Additionally, the outliers are much higher (almost 40k versus 20k). For the Lasso model, however, the smallest prediction for money spending is 1'705, which is also not reasonable. In comparison the Lasso model is still more reasonable.