---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "15.12.2021"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('Group 1 GHA 3.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required libraries and the data sets are loaded 
first.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
The average online spending is $1959.921
```{r exercise_1, echo=TRUE, warning=FALSE}
```

# Exercise 2 {-}
The household with id = 1297 (first row of the 2006 sample) spends most of the time on *weather.com*
```{r exercise_2, echo=TRUE, warning=FALSE}
```


# Exercise 3 {-}
To find the best two linear predictors, lasso was used. First, a 5-fold cross 
validation was performed to determine the optimal lambda parameter. Then, the largest 
coefficients of the lasso model in terms of their absolute value were determined, since 
they have the greatest influence on the prediction. The best two linear predictors are 
therefore the two websites *staples.com* and *officedepot.com*.
```{r exercise_3, echo=TRUE, warning=FALSE}
```
