---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "13 5 2020"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('code.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required library and the data set are loaded first. 
The library *ggplot2* is used for plotting various graphics.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
The number of observations in the data set corresponds to the number of rows and the 
number of covariates collected corresponds to the number of columns minus one 
(dependent variable). Thus there are 1204 observations and 6 covariates.
```{r exercise_1, echo=TRUE, warning=FALSE}
```

# Exercise 2 {-}
The highest number of children who are covered by one health insurance is 5.
```{r exercise_2, echo=TRUE, warning=FALSE}
```

# Exercise 3 {-}
The region *northwest* has the lowest share of smokers. The share of smokers in this 
region is 16.9 percent.
```{r exercise_3, echo=TRUE, warning=FALSE}
```

# Exercise 4 {-}
According to the plot, two patterns can be identified in the data. It can be seen that 
the older the primary beneficiary, the higher the individual medical costs billed by 
health insurance. This makes sense because the likelihood of health problems increases 
with age. Furthermore, it can be seen that the average medical costs billed by health 
insurance are higher for the group of smokers than for the group of non-smokers. This 
also makes sense, as smoking increases the likelihood of health problems. It can be 
assumed that the area where the average medical costs billed by health insurance of 
smokers and non-smokers overlap can be explained by other covariates.
```{r exercise_4, echo=TRUE, warning=FALSE, fig.align='center'}
```

\pagebreak

# Exercise 5 {-}
The plot shows that the body mass index and the medical costs billed by health 
insurance are positively related. This makes sense, as being overweight increases the 
risk of health problems. One might have expected the relationship to be even stronger. 
It can be assumed that this can be explained by other covariates.
```{r exercise_5, echo=TRUE, warning=FALSE, fig.align='center'}
```

# Exercise 6 {-}
According to the boxplot below, the median body mass index is higher in the southern 
regions than in the northern regions. The high median body mass index of the southeast 
region is particularly striking. The median body mass index is above 24.9 (maximum 
value of an ideal bmi) in all regions, which may be a cause for concern.
```{r exercise_6, echo=TRUE, warning=FALSE, fig.align='center'}
```