---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "13 5 2020"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('code.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required library and the data set are loaded first. 
The library *ggplot2* is used for plotting various graphics.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
The number of observations in the data set corresponds to the number of rows and the 
number of covariates collected corresponds to the number of columns minus one 
(dependent variable). Thus there are 1204 observations and 6 covariates.
```{r exercise_1, echo=TRUE, warning=FALSE,}
```

# Exercise 2 {-}
The highest number of children who are covered by one health insurance is 5.
```{r exercise_2, echo=TRUE, warning=FALSE,}
```

# Exercise 3 {-}
The region *northwest* has the lowest share of smokers. The share of smokers in this 
region is 16.9 percent.
```{r exercise_3, echo=TRUE, warning=FALSE,}
```