---
author: "Cyril Janak, Jonas Husmann, Niklas Kampe, Robin Scherrer"
date: "08.12.2021"
geometry: "left= 2cm, right = 2cm, top = 2.5cm, bottom = 2.5cm"
output: 
   pdf_document:
      includes:
         in_header: rmarkdown/style.sty
      number_sections: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::read_chunk('Group 1 GHA 2.R')
```

\thispagestyle{empty}
\input{rmarkdown/titlepage.tex}

\pagebreak

\thispagestyle{empty}
\tableofcontents

\pagebreak
\setcounter{page}{1}

# Requirements {-}
To solve the following tasks, the required libraries and the data sets are loaded 
first.
```{r requirements, echo=TRUE, warning=FALSE}
```

# Exercise 1 {-}
There are 214 observations in the training data set and 143 observations in the test 
data set.
```{r exercise_1, echo=TRUE, warning=FALSE}
```

# Exercise 2 {-}
The average grade is ~11.64, the minimum grade is 4 and the maximum grade is 19. All 
numbers were calculated using the training data.
```{r exercise_2, echo=TRUE, warning=FALSE}
```